---
output: github_document
---
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# TABS: An R Package

This package provides an easier way to import project data from the Texas Architectural Barriers System database maintained by the [Texas Department of Licensing and Regulation](https://www.tdlr.texas.gov/).

### Installation

You can install the development version of TABS from [GitHub](https:://github.com/aberuiz/TABS) with:

```{r, message=FALSE, warning=FALSE}
#install.packages("remotes")
remotes::install_github("aberuiz/TABS")
library(TABS)
```

## Usage

The package works primarily around one function to receive projects registered with TABS: `GetProjects`.

The example below will pull all projects registered within Travis County on February 29, 2024.
```{r}
GetProjects(
  county = "Travis",
  reg_begin = "02/29/24",
  reg_end = "03/01/24"
)
```

## Additional Arguments

In addition to dates you can search for projects by county, city, address, owner name, facility, and/or project name. The below example will search for all projects in the City of Austin that are owned by Tesla.
```{r}
GetProjects(
  city = "Austin",
  owner = "Tesla"
)
```

### Details

**Registration Dates:**

Dates are required to be in the mm/dd/yy format. For automating dates, you can use `format(Sys.Date(), "%D")`.
Date arguments are passed to the database as midnight therefore, `reg_begin` at 02/29/24 will include projects starting on February 29, 2024 and `reg_end` at 03/01/24 will mean projects that started on 03/01/24 or later will not be included.
   
**Name Matching**

City and county names are matched case-insensitively, and surrounding whitespace is ignored, so capitalization no longer needs to match. Spelling and internal spacing must still match how TDLR lists the name (for example, `"De Witt"`, not `"Dewitt"`).

**Completeness and request controls**

By default, `GetProjects()` warns if it cannot verify completeness and returns
available results. Repeated pages are excluded. For a job that saves checkpoints,
use `strict = TRUE` so incomplete searches raise an error before the job marks
them complete. Valid empty searches still warn and return invisible `NULL`.
HTTP and JSON parsing errors propagate in either mode.

```{r, eval=FALSE}
projects <- GetProjects(
  county = "Travis",
  reg_begin = "02/01/24",
  reg_end = "03/01/24",
  strict = TRUE,
  request_interval = 1.5,
  timeout = 60,
  user_agent = "My project (contact: maintainer@example.org)"
)
```

Requests, including retries, are paced within each R session at 1.5 seconds by
default; use `request_interval = 0` to disable pacing. Separate R processes do
not share this limit. `timeout` applies to each HTTP attempt and defaults to
`NULL`, preserving the existing timeout behavior. The default User-Agent remains
the TABS package identifier; callers can pass their configured contact explicitly.
Completeness checks cannot guarantee a snapshot of a changing database.

To install a specific release, including the previous version if needed:

```{r, eval=FALSE}
remotes::install_github("aberuiz/TABS@v0.1.5")
# Revert to the version before the completeness and pacing changes:
remotes::install_github("aberuiz/TABS@v0.1.4")
```

Restart R after installation to load the selected version. Pin a tag in automated
jobs to keep future releases from changing their behavior unexpectedly.
